Modeling the Java Card API in B

### 2012-04-02 trunk/papers/B2012-work/javacardAPIpaper.tex
secao 4 - adicionado texto

\section{B specification of the Java Card API}

@@

>>>>

\section{B specification of the Java Card API}\label{sec:api-spec}

@@

The models are used in the different phases of the 
BSmart method development. Initially, the application 
abstract specification uses the models of basic Java types, 
since Java Card specific aspects are ideally related only
in subsequent refinements.

The BSmart Full Function refinement introduces the modelling of exceptions, 
as stated in section~\ref{sec:api-spec}. This is performed through  the inclusion
of \emph{ISOException} machine, which receives, in its \emph{throwIt} operation, 
a short value corresponding to the \emph{status} code that must be returned to 
the client when the conditions are not satisfied.

In the B implementation, the whole set of the API can be related. Usually, besides
ISOException (or other exception model), in a typical Java Card development 
are imported \emph{Apdu} and \emph{Util}  modules. The fist defines operations
to start the process of receiving (from host) and sending (to host) information 
through the \emph{apdu buffer}. The preconditions of these sending/receiving 
operations aid the verification process, since the specifier must to observe 
the correct order in operation calling. The \emph{Util} component contains useful 
operations to effectively get and put data in the buffer. When translating to 
\emph{Java Card} the operation calling are translated to the corresponding 
\emph{Java Card} method.
